---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "Jule Krüger, Dana King"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, include=FALSE}
library(tidyverse)
```
# Introduction
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status. We hypothesize that  life expectancy increases with a country's GDP.

```{r load_data, include=FALSE, echo=TRUE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

# Results

## My plot
```{r plot_gdp_lifeexp, echo=FALSE}
ggplot(data=gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp) +
  geom_point()
```

```{r calculate_summary_statistics, include=FALSE}
nCountries <- gapminder_1997 %>% 
  select(country) %>% 
  n_distinct()

minGDP <- gapminder_1997 %>% 
  summarise(round(min(gdpPercap)))

maxGDP <- gapminder_1997 %>% 
  summarise(round(max(gdpPercap)))

```

For this analysis, `r nCountries` countries were analyzed for this report. The minimum GDP per capita was `r minGDP`, the maximum GPD per capita was `r maxGDP`.

| Indicator  |  Value |
|---|---|
|  Minimum GDP | `r minGDP`   |
|  Mean GDP | |
|  Maximum GDP |  `r maxGDP` |

```{r make_table_with_kable, echo=FALSE}
gapminder_1997 %>% 
  filter(continent=="Oceania") %>% 
  knitr::kable()
```


